%Modified template for a CV. Not pretty code, in fact not great code, but it works.

%%%%%

\documentclass{resume} % Use the custom resume.cls style
 \usepackage{bibentry}
%\usepackage{times}
\usepackage[T1]{fontenc}
 \usepackage[hidelinks]{hyperref}
\usepackage{url}
\urlstyle{tt}
\usepackage{etaremune}
\usepackage[left=1 in,top=1in,right=1 in,bottom=1in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\updateinfo}[1][\today]{\par\vfill{\textit{Last updated on #1}}}
\name{Dylan Schlichting} % Your name

\pagenumbering{Roman}
\pagestyle{plain}
\begin{document}
\begin{minipage}[ht]{0.35\textwidth}
  \href{http://www.tamu.edu/}{Texas A\&M University} \\
  \href{http://ocean.tamu.edu/}{Department of Oceanography} \\
  618 Eller O$\&$M Building  \\
  College Station, TX 77843-3146
\end{minipage}
\begin{minipage}[ht]{0.6\textwidth}
  \href{mailto:dylan.schlichting@tamu.edu}{dylan.schlichting@tamu.edu} \\
  (413) 262-4393\\
  \url{https://dylanschlichting.github.io/}
  \updateinfo
\end{minipage}
\vspace{-65 pt}
\bibliographystyle{apalike}
\nobibliography{Manuscripts}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{60pt}
\begin{rSection}{Education}

Ph.D. Oceanography, Texas A$\&$M 
University \hfill {Jan 2020 - Aug 2024 (Expected)
}
\\
\textit{Advisors}: Drs. Robert Hetland $\&$ Henry Potter
\\
\\
B.S. Civil Engineering, University of Maine \hfill {Aug 2016 - Dec 2019}
\\ 
{\textit{Minor}:} Mathematics
\end{rSection}

%	WORK EXPERIENCE SECTION
\begin{rSection}{Research Experience}
\begin{rSubsection}{Graduate Research Assistant}{Jan 2020 - Present}{Texas A$\&$M University: Dept. Oceanography}{} 
\item Characterized numerical tracer mixing in a high-resolution ocean model of the Texas-Louisiana continental shelf.
\item Developed idealized numerical simulations with the Regional Ocean Modeling System (ROMS) for further analysis of numerical mixing.
\item Helped develop the concept of mixing pathways for characterizing tracer mixing.
\item Provided shore support for two oceanographic cruises in 2021/2022 as part of the Submesoscales Under Near-Resonant Inertial Shear Experiment (SUNRISE, \url{https://sunrise-nsf.github.io/}).
\end{rSubsection}    

\begin{rSubsection}{Student Research Assistant}{May 2017 - Dec 2019}{UMaine: Dept. Civil Engineering}{} 
\item Used analytical modeling to study the interaction of flow and suspended kelp farms.  
\item Analyzed the environmental impacts of coastal armoring structures on pocket beaches in Southern Maine.
\item Participated in the construction, deployment, and management of an oceanographic mooring system for the Sensing Storm Surge Citizen Science Project. (\url{http://sensingstormsurge.acg.maine.edu/}).
\item Designed and co-managed laboratory experiments to study hydrodynamic and turbulent characteristics of flow through floating oyster cages.
\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{Engineering Research Assistant}{Aug 2018 - May 2019}{UMaine: School of Marine Sciences}{}
\item Characterized inertial oscillations in the Gulf of Maine using observational data.
\item Used spectral analysis to study ocean circulation in the Gulf of Maine.
\end{rSubsection}

\begin{rSubsection}{Research Experience for Undergraduates}{May 2018 - Aug 2018}{Texas A$\&$M University: Dept. Oceanography}{} 
\item Characterized salinity structure in Copano Bay, TX using ROMS model output.
\item Analyzed time scales, total exchange flow, and salinity variance in Copano Bay to improve performance of existing numerical models.
\item Cruise: R/V Pelican (3 days). Cocodrie, LA, to Flower Garden Banks National Marine Sanctuary in the northern Gulf of Mexico.
\end{rSubsection} 
\end{rSection} 
\vspace{-3pt}

\begin{rSection}{Research Interests}
\vspace{-10pt}
\item High resolution coastal ocean modeling, spurious mixing, submesoscale processes and dynamics, estuarine exchange flow and mixing.

\end{rSection}

\begin{rSection}{Publications}
\vspace{-3pt}

\begin{etaremune}
\item \textbf{Schlichting, D.}, Qu, L., Kobashi, D., \& Hetland, R. (2023). Quantification of physical and numerical mixing in a coastal ocean model using salinity variance budgets. \textit{Journal of Advances in Modeling Earth Systems},
15, e2022MS003380. \url{https://doi.org/10.1029/2022MS003380}.
\item Qu, L., Hetland, R., \& \textbf{Schlichting, D.} Mixing pathways in simple box models (2022). \textit{Journal of Physical Oceanography}, 52(11), 2761-2772. \url{https://doi.org/10.1175/JPO-D-22-0074.1}.
\item Spicer, P., \textbf{Schlichting, D.}, Huguenard, K., Roche, A., \& Rickard, L. (2021). Sensing Storm Surge: A framework for establishing a citizen scientist monitored water level network. \textit{Ocean and Coastal Management}, 211, 105802. \url{https://doi.org/10.1016/j.ocecoaman.2021.105802}.
\end{etaremune}
\end{rSection}

\begin{rSection}{Manuscripts in preparation}
\vspace{-3pt}
\begin{etaremune}
\item Wei Hsu, F., Shearman, R. Kipp , \textbf{Schlichting, D.}, Kobashi, D., \& Hetland, R. $S_2$ Atmospheric Tide Driven Superinertial Oscillation on the Texas-Louisiana Shelf. Intent to submit to \textit{Journal of Physical Oceanography}.
\end{etaremune}
\end{rSection}

\begin{rSection}{Invited talks/lectures}
\vspace{-3pt}

\begin{etaremune}
    \item \textbf{Schlichting, D.} (2022). An introduction to numerical mixing in a coastal ocean model of the Texas-Louisiana continental shelf. Submesoscales under near-resonant inertial shear experiment (SUNRISE) meeting. December 11. Bend, OR.
    \item \textbf{Schlichting, D.}, Qu, L., Hetland, R., \& Kobashi, D. (2022). Quantification of physical and numerical mixing using tracer variance dissipation in a coastal ocean model. Pacific Northwest National Laboratory coastal modeling group. July 11.
\end{etaremune}
\end{rSection}

\begin{rSection}{Academic Presentations} \itemsep -3pt
\begin{etaremune}
    \item \textbf{Schlichting, D.}, \& Hetland, R. (2023). Numerical mixing in idealized simulations of baroclinic instabilities over a shelf. Gordon Research Seminar/Conference on coastal ocean dynamics, June 17-23. Poster.
    \item \textbf{Schlichting, D.}, Qu, L., Hetland, R., \& Kobashi, D. (2022). Quantification of physical and numerical mixing using tracer variance dissipation in a coastal ocean model. Gordon Research Seminar/Conference on ocean mixing, June 4-10. Poster.
    \item Hetland, R., Qu, L., \& \textbf{Schlichting, D.} (2022). Tracer variance mixing in simple box models. Ocean Sciences Meeting. February 24 - March 4. Talk.
    \item \textbf{Schlichting, D.}, Qu, L., Hetland, R., \& Kobashi, D. (2022). Using salinity variance budgets to quantify numerical mixing in a coastal ocean model. Ocean Sciences Meeting. February 24 - March 4. Talk. 
    \item \textbf{Schlichting, D.}, Hetland, R., Qu, L., \& Kobashi, D. (2021). Using tracer variance budgets to quantify numerical mixing offline in a coastal ocean model. Warnem\"{u}nde Turbulence Days Meeting. December 6-9. Talk. 
    \item \textbf{Schlichting, D.}, Lieberthal, B., \& Huguenard, K. (2019). An assessment into vegetation farms as a solution to coastal erosion in southern Maine. Northeast Aquaculture Conference, Boston MA. January 9-11. Poster.
    \item \textbf{Schlichting, D.} \& Hetland, R. (2018). Using salinity variance and total exchange flow to analyze salinity structure in an unsteady estuary. Physics of Estuaries and Coastal Seas Conference, Galveston TX. October 14-18. Poster.
    \item \textbf{Schlichting, D.} \& Hetland, R. (2018). Mechanisms controlling salinity structure structure in a broad, shallow, unsteady estuary. Sustainable Ecological Aquaculture Network Undergraduate Research Symposium, Walpole ME. August 7. Poster.
    \item \textbf{Schlichting, D.} \& Hetland, R. (2018). Salinity structure in Copano Bay. Texas A$\&$M University Observing the Ocean REU Student Symposium, College Station, TX. August 2. Talk.
    \item \textbf{Schlichting, D.}, Lieberthal, B., \& Huguenard, K. (2017). Vegetation farms as a solution to coastal erosion for Saco, Maine. Sustainable Ecological Aquaculture Network Undergraduate Research Symposium, Walpole ME. August 16. Poster.
\end{etaremune}
\end{rSection}

\begin{rSection}{Additional conferences/workshops} \itemsep -3pt
\begin{etaremune}
    \item Texas Center for Climate Studies High Resolution Earth System Modelling Workshop (2023). College Station, TX, January 23-25. 
    \item Scientific Computing with Python Conference (2021). July 12-18. \textit{Virtual}. 
    \item Scientific Computing with Python Conference (2020). July 6-12.  \textit{Virtual}.
    \item Coastal and Estuarine Research Federation Conference (2017). Providence, RI, November 5-9.
\end{etaremune}
\end{rSection}

\begin{rSection}{Service and teaching}
Reviewer: \textit{Journal of Advances in Modeling Earth Systems} \hfill Aug. 2023 - Present \\
Reviewer: \textit{Journal of Geophysical Research: Oceans} \hfill Aug. 2023 - Present \\
Judge: Student Research Week (two 2 hour sessions) \hfill Spring 2023 \\
NSF PROGRESS Mentor \hfill Fall 2022 \\
Judge: Environmental Geosciences (GEOS 405, TAMU) \hfill Spring 2022 \\
Tutor: Computers in Civil Engineering (CIE 115, UMaine) \hfill Spring 2019 \\
\end{rSection}
\vspace{-10pt}
%----------------------------------------------
\begin{rSection}{Honors and Awards} \itemsep -3pt {}
\vspace{-7pt}
\item Louis and Elizabeth Scherck Scholarship (X4) \hfill 2020-Present
\item NSF S-STEM Scholar (X2) \hfill Jan 2020 - Aug 2021 
\item Oceanography Graduate Council mini-grant recipient (X3) \hfill 2021
\item Frank Sleeper - Sawyer Scholarship \hfill 2017 - 2019
\item Best capstone project \hfill 2019
\item Chi Epsilon Member: Civ. Eng. Honors Society \hfill 2019 
\item NSF Research Experience for Undergraduates Scholar \hfill May 2018 - Aug 2018
\item Alpha Tau Omega Memorial Scholarship \hfill 2018
\end{rSection}

\begin{rSection}{SKILLS}
\begin{itemize}
%\begin{rSubsection}{Computing and Programming}{}{}{} 
    \item High-level programming languages: Python (advanced), Matlab (intermediate), \LaTeX (advanced), Markdown (advanced), FORTRAN (basic), C$++$ (basic).
    \item Proficient in Linux administration.
    \item Website design with GitHub Pages, HTML, Ruby, and CSS.
    \item Ocean modeling: Realistic and idealized simulations with ROMS and COAWST. Basic knowledge of MPAS-O and FVCOM. 
    \item Civil engineering: Basic experience with HEC-RAS, AutoCad, and Revit.
\end{itemize}
%\item Basic knowledge of Gener
%\end{rSubsection}
%\begin{rSubsection}{Civil Engineering}{}{}{} 
%\item Experience with Autocad, Revit, HEC-RAS, and Microsoft Project
%\end{rSubsection}
\end{rSection}

\begin{rSection}{Professional Societies} \itemsep -3pt {}
\begin{itemize}
    \item American Geophysical Union
    \item Association for the Sciences of Limnology and Oceanography
    \item The Oceanography Society 
    \item American Society of Civil Engineers
\end{itemize}
\end{rSection}


%----------------------------------------------------------------------------------------

\end{document}
