%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
 \usepackage{bibentry}
 \usepackage{times}
% \renewcommand\familydefault{\sfdefault} 
% \usepackage[T1]{fontenc}

\usepackage[left=0.75 in,top=0.75in,right=0.75 in,bottom=0.75in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Dylan Schlichting} % Your name
\address{University of Maine, Boardman Hall, Orono, ME 04469} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{+1-413-262-4393 \\ dylan.schlichting@maine.edu}  % Your phone number and email

\begin{document}
\bibliographystyle{apalike}
\nobibliography{Presentations}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Science: Civil Engineering} \hfill {August 2016 - December 2019}
\\ 
{\bf Minor: Mathematics}
\\
University of Maine: GPA 3.405 / 4.0 
\\
Relevant Coursework: Physical Oceanography (Graduate), Open Channel Hydraulics, Introductory Structural Analysis, Soil Mechanics

\end{rSection}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
\begin{rSubsection}{Student Research Assistant}{May 2017 - Present}{UMaine: Dept. Civil Engineering}{Advisor: Dr. Kimberly Huguenard} 
\item First author of an \textit{in-prep} technical report assessing vegetation farms as a solution to coastal erosion in Southern Maine
\item Experience studying coastal loading on structures and the impacts of coastal structures on sediment transport
\item Co-managed the field work component of the Sensing Storm Surge Citizen Science Program
\item Communicated with citizen scientists on a weekly basis and organized project metadata
\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{Research Experience for Undergraduates}{May 2018 - August 2018}{Texas A$\&$M University: Dept. Oceanography}{Advisor: Dr. Robert Hetland} 
\item Analyzed Regional Ocean Modeling Systems outputs in Python to study estuarine dynamics in Copano Bay, TX
\item Participated in a research cruise on the R/V Pelican (3 days). Cocodrie, LA, to Flower Garden Banks National Marine Sanctuary. Conducted nutrient, salinity, and methane sampling.
\item Presented three posters and one talk at research symposiums/conferences.
\end{rSubsection} 

\end{rSection} 

\begin{rSection}{Honors/Awards} \itemsep -3pt {}
\vspace{-7pt}
\item Chi Epsilon: Civil Engineering National Honors Society \hfill 2019 - present
\item Alpha Tau Omega Memorial Scholarship \hfill 2019 - present
\item Frank Sleeper-Sawyer Scholarship \hfill 2016 - present

\item First undergraduate to present at the Physics of Estuaries and Coastal Seas Conference \hfill Oct. 2018
\item Attended the Coastal and Estuarine Research Federation Conference
\item Dean's List \hfill Fall 2016
\end{rSection}

\begin{rSection}{SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming & MatLab (Advanced), Python (Intermediate), R (Rudimentary) \\
Sotfware & Autocad, Revit, HEC-RAS, \LaTeX, Wolfram Mathematica, Microsoft Project,  

\end{tabular}
\end{rSection}
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} \itemsep -1pt {}   
\vspace{-7pt}
\item Alpha Tau Omega \hfill Fall 2017 - Present
\item American Society of Civil Engineers \hfill Fall 2017 - Present 
\item Engineers Without Borders \hfill Fall 2016
\end{rSection}
\end{document}
